---
title: "John's Picks"
---

```{r setup, include=FALSE}
library(kableExtra)
options(kableExtra.html.bsTable = TRUE)
library(tidyverse)
library(lubridate)
library(gt)
date <- Sys.Date()
make_hyperlink = function(myurl,mytext) {
  paste('<a href=',myurl,'>',mytext,'</a>')
}
```

```{css, echo = FALSE}
.video-box {
  position: relative;
  overflow: hidden;
  width: 100%
}
/*  padding-top: 56.25%; /* 16:9 Aspect Ratio (divide 9 by 16 = 0.5625) */

/* Then style the iframe to fit in the container div with full height and width */
.responsive-iframe {
  position: absolute;
  top: 0;
  left: 0;
  bottom: 0;
  right: 0;
  width: 100%;
  height: 100%;
}
```

# Welcome to John's Picks!

## Background

John has been going to a lot of shows alone. 

There's nothing wrong with that. 

In fact, it's so easy - and he's so into it - he's having trouble not doing it. 

This website is an effort towards making his evening plans openly available to those he would love any opportunity to see. 

The link under Seat links to the ticket page, and if you would like to join my Google Calendar event you can click the button to its right.

## Picks

```{r, echo = F, warning=FALSE}
options(kableExtra.html.bsTable = TRUE)
picks <- read.csv('../static/picks.csv')
locations <- read.csv('../static/locations.csv')
picks <- merge.data.frame(picks, locations)

picks %>%
  # mutate(Embedding = paste0("<div class=\"video-box\">
  #                                    <iframe class=\"responsive-iframe\"
  #                                    src=",Embedding,">
  #                                    </iframe></div>"),
  mutate("Event_Embedding" = map(Event_Embedding, gt::html)) %>%
  rename("Add Event" = Event_Embedding) %>%
  mutate(Location = make_hyperlink(Location_Embedding, Location),
         Seat = make_hyperlink(Ticket_Embedding, Seat)) %>%
  gt() %>%
  fmt (
    columns = c('Location','Seat'),
    fns = function(x) sapply(x, htmltools::HTML)) %>%
  cols_hide(c(Location_Embedding, Ticket_Embedding))
                   
```
