---
title: "John's Picks"
---

```{r setup, include=FALSE}
library(kableExtra)
options(kableExtra.html.bsTable = TRUE)
library(tidyverse)
library(lubridate)
library(gt)
date <- Sys.Date()
make_hyperlink = function(myurl,mytext) {
  paste('<a href=', myurl,' target="_blank">',mytext,'</a>')
}
```

```{css, echo = FALSE}
.video-box {
  position: relative;
  overflow: hidden;
  height: 100%;
  min-height: 200px;
  min-width: 150px;
  width: 100%
}
/*  padding-top: 56.25%; /* 16:9 Aspect Ratio (divide 9 by 16 = 0.5625) */

/* Then style the iframe to fit in the container div with full height and width */
.responsive-iframe {
  position: absolute;
  top: 0;
  left: 0;
  bottom: 0;
  right: 0;
  width: 100%;
  height: 100%
}
```

# Welcome to John's Picks!

## Background

This website is an effort in making John's evening plans openly available to those he would welcome any opportunity to see. If you are seeing this, you are a person John would be happy to see in most any context, and particularly for any plans he has listed here.

The text under the Seat column links to the ticket page, the code is:

- **GA** : I have bought a ticket and it's general admission
- **Not yet** : I have not bought a ticket yet
- **Seat number** : I have bought a ticket and it has the given seat number
- **Door** : You can only pay at the door 
- **Door (cash)** : You can only pay at the door in cash

and if you would like to join the Google Calendar event you can click the button under each row

## Picks

```{r, echo = F, warning=FALSE}
options(kableExtra.html.bsTable = TRUE)
picks <- readxl::read_xlsx('../static/picks.xlsx')
locations <- read.csv('../static/locations.csv')
picks <- merge.data.frame(picks, locations, all.x = T) %>%
  mutate(Time = format(Time, "%H:%M")) %>%
  arrange(Date, Time)

picks %>%
  mutate(Maps_Embedding = paste0("<div class=\"video-box\">
                                     <iframe class=\"responsive-iframe\"
                                     src=",Maps_Embedding,">
                                     </iframe></div>"),
  Event_Embedding = map(Event_Embedding, gt::html),
  Maps_Embedding = map(Maps_Embedding, gt::html)) %>%
  rename("Add Event" = Event_Embedding,
         "Map" = Maps_Embedding) %>%
  mutate(Location = make_hyperlink(Location_Embedding, Location),
         Seat = make_hyperlink(Ticket_Embedding, Seat)) %>%
  unite("When", c("Date", "Time"), sep = " ") %>%
  gt() %>%
  opt_interactive(use_highlight = T) %>%
  fmt (
    columns = c('Location','Seat'),
    fns = function(x) sapply(x, htmltools::HTML)) %>%
  cols_hide(c(Location_Embedding, Ticket_Embedding, Location)) %>%
  cols_width("Add Event" ~ px(100),
             Description ~ px(200)) %>%
  opt_stylize(style = 3)
                   
```
